The Correspondence Analysis of Two Mode Networks Revisited

### 2025-02-20 main-R1.tex

\begin{figure}[ht!]
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/p-norm.png}
            \caption{Degree-weighted projection (People).}
            \label{fig:ca-reord}
    \end{subfigure}
     \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/g-norm.png}
            \caption{Degree-weighted projection (Groups).}
            \label{fig:bon-reord}
    \end{subfigure}
    \caption{Degree-weighted projection matrices of the Southern Women data.}
    \label{fig:dwproj}
\end{figure}

@@

\begin{figure}
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/p-ca-ref-corr.png}
            \caption{CA/Reflection Correlation (Persons).}
            \label{fig:p-ca-ref}
    \end{subfigure}
     \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/g-ca-ref-corr.png}
            \caption{CA/Reflection Correlation (Groups)}
            \label{fig:g-ca-ref}
    \end{subfigure}
    \caption{Scatter plot of the scores computed by the method of reflections ($q = 26$) on the y-axis and the first dimension of the Correspondence Analysis of the two-mode affiliation matrix on the x-axis, for both persons (a) and groups (b). }
    \label{fig:ca-ref-corr}
\end{figure}

@@

\begin{figure}[ht!]
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/ca-reord.png}
            \caption{Re-ordered Affiliation matrix (CA First Dimension).}
            \label{fig:ca-reord}
    \end{subfigure}
     \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/bon-reord1.png}
            \caption{Re-ordered Affiliation matrix (Bonacich Centrality).}
            \label{fig:bon-reord1}
    \end{subfigure}
     \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/bon-reord2.png}
            \caption{Re-ordered Affiliation matrix (Bonacich Second Dimension).}
            \label{fig:bon-reord2}
    \end{subfigure}
    \caption{Southern Women Affiliation matrix with re-ordered rows and columns: (a) row and columns re-ordered according to the person and group score on the first CA dimension, (b) row and columns re-ordered according to person and group Eigenvector centrality score, (c) row and columns re-ordered according to person and group score on the second Bonacich dimension.}
    \label{fig:ca-v-bon}
\end{figure}

@@

\begin{figure}
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/p-ca-eigvec.png}
            \caption{Eigenvector plot (Persons).}
            \label{fig:p-eigvec}
    \end{subfigure}
     \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/g-ca-eigvec.png}
            \caption{Eigenvector plot (Groups).}
            \label{fig:g-eigvec}
    \end{subfigure}
    \caption{CA Eigenvector plot for persons (a) and groups (b). The first CA score is on the x-axis, and the rank order of persons and groups is on the y-axis. Insets show the eigenvalue orderings on the x-axis ($k$) for persons and groups.}
    \label{fig:ca-eigvec}
\end{figure}

>>>>

\begin{figure}[ht!]
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.55\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/p-norm.png}
            %\caption{Degree-weighted projection (People).}
            %\label{fig:ca-reord}
    \end{subfigure} \\
     \begin{subfigure}[b]{0.55\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/g-norm.png}
            %\caption{Degree-weighted projection (Groups).}
            %\label{fig:bon-reord}
    \end{subfigure}
    \caption{Degree-weighted projection matrices of the Southern Women data.}
    \label{fig:dwproj}
\end{figure}

@@

\begin{figure}
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/p-ca-ref-corr.png}
            \caption{}
            \label{fig:p-ca-ref}
    \end{subfigure}
     \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/g-ca-ref-corr.png}
            \caption{}
            \label{fig:g-ca-ref}
    \end{subfigure}
    \caption{Scatter plot of the scores computed by the method of reflections ($q = 26$) on the y-axis and the first dimension of the Correspondence Analysis of the two-mode affiliation matrix on the x-axis, for both persons (a) and groups (b). }
    \label{fig:ca-ref-corr}
\end{figure}

@@

\begin{figure}[ht!]
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/ca-reord.png}
            \caption{}
            \label{fig:ca-reord}
    \end{subfigure}
     \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/bon-reord1.png}
            \caption{}
            \label{fig:bon-reord1}
    \end{subfigure}
     \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/bon-reord2.png}
            \caption{}
            \label{fig:bon-reord2}
    \end{subfigure}
    \caption{Southern Women Affiliation matrix with re-ordered rows and columns: (a) row and columns re-ordered according to the person and group score on the first CA dimension, (b) row and columns re-ordered according to person and group Eigenvector centrality score, (c) row and columns re-ordered according to person and group score on the second Bonacich dimension.}
    \label{fig:ca-v-bon}
\end{figure}

@@

\begin{figure}
    \centering
        \includegraphics[width=1.0\textwidth]{Plots/ca-eigvec.png}            
        \label{fig:eigvec}
    \caption{CA Eigenvector plot for persons (a) and groups (b). The first CA score is on the x-axis, and the rank order of persons and groups is on the y-axis. The inset plot (c) shows the eigenvalue orderings on the x-axis ($k$) for persons and groups.}
    \label{fig:ca-eigvec}
\end{figure}
